Crystal as a thermodynamic computer

### 2024-09-04 paper/main.tex
update

We conducted numerical experiments both for energy-gradient and wave-packet scheme, under the condition
$\Lambda = 1.3, n = 15$ , and fitted each sweep time against
$m \log^2(m)$. Where $m$ represents the number of the single layers,
$n$ represents the width per single layer.

>>>>

\ym{I will move this figure to AppendixB to show the equivalent 
between heat bath and energy gradient. Another plot would be put here that
show the TL v.s. $m\ln^{1+\frac{1}{c\ln(\Lambda)}}m$}
We conducted numerical experiments both for energy-gradient and wave-packet scheme, under the condition
$\Lambda = 1.3, n = 15$ , and fitted each sweep time against
$m \log^2(m)$. Where $m$ represents the number of the single layers,
$n$ represents the width per single layer.
